### 2018-05-09 Paper/examples.tex
..

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/sense_borehole}
  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_borehole}
\caption{
Left: Sobol' total sensitivity index for uncertain parameters in the borehole
function. Right: 
estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$) is plotted
against number of samples considered for evaluating $\mu_i$. Corresponding estimates
for the converged Sobol' total effect index ($\mathcal{T}(\theta_i)$) in each case is also included in the
legend. \alennote{Can we have larger fontsizes for the right image? Also the y-axis label
needs to be modified with a widehat as done in the text now.}}
\label{fig:sense_bore}
\end{center}
\end{figure}
In Figure~\ref{fig:sense_bore}~(right), we plot estimates of the screening parameter 
$\widehat{\mathcal{C}_i\mu_i}$ for a wide range of the number of 
samples used for approximating $\mu_i$ using~\eqref{eq:mu}.
Estimates for $\widehat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$ even when small number of samples (5--10) are used. 
Consequently, the relative importance of uncertain 
parameters in the borehole function is found to be consistent 
with predictions based on the Sobol' index. 
In the considered intervals for the uncertain parameters, it is clear 
that the discharge is insensitive to $T_u$ and $T_l$. 
Moreover, the sensitivity to $K_w$ is also small. We exploit these findings to reduce
the dimensionality of the problem by 
discounting the uncertainties in $T_u$, $T_l$, and $K_w$ by fixing 
them at their respective nominal values.

>>>>

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/sense_borehole}
  \includegraphics[width=0.51\textwidth]{./Figures/ub_conv_borehole}
\caption{
Left: Sobol' total sensitivity index for uncertain parameters in the borehole
function. Right: 
estimates of the screening parameter ($\widehat{\mathcal{C}_i\mu_i}$) is plotted
against number of samples considered for evaluating $\mu_i$. Corresponding estimates
for the converged Sobol' total effect index ($\mathcal{T}(\theta_i)$) in each case is also included in the
legend. }
\label{fig:sense_bore}
\end{center}
\end{figure}
In Figure~\ref{fig:sense_bore}~(right), we plot estimates of the screening parameter 
$\widehat{\mathcal{C}_i\mu_i}$ for a wide range of the number of 
samples used for approximating $\mu_i$ using~\eqref{eq:mu}.
Estimates for $\widehat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$ even when small number of samples (5--10) are used. 
Consequently, the relative importance of uncertain 
parameters in the borehole function is found to be consistent 
with predictions based on the Sobol' index. 
In the considered intervals for the uncertain parameters, it is clear 
that the discharge is insensitive to $T_u$ and $T_l$. 
Moreover, the sensitivity to $K_w$ is also small. We exploit these findings to reduce
the dimensionality of the problem by 
discounting the uncertainties in $T_u$, $T_l$, and $K_w$ by fixing 
them at their respective nominal values.
